Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-09-08 forgerard.tex
comments after videocon addressed.

\documentclass{aastex}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{lineno}
\linenumbers

@@

\title{Evidence for an Intrinsic Color Parameter in Type~Ia Supernovae}
\author
{
    A.~G.~Kim,\altaffilmark{1}
    G.~Smadja,\altaffilmark{2} 
    G.~Aldering,\altaffilmark{1}
    P.~Antilogus,\altaffilmark{4}
    S.~Bailey,\altaffilmark{1}
    C.~Baltay,\altaffilmark{5}
    K.~Barbary,\altaffilmark{3}
    D.~Baugh,\altaffilmark{6}
    K.~Boone,\altaffilmark{1,3}
    S.~Bongard,\altaffilmark{4}
    C.~Buton,\altaffilmark{2}
    J.~Chen,\altaffilmark{6}
    N.~Chotard,\altaffilmark{2}
    Y.~Copin,\altaffilmark{2}
    P.~Fagrelius,\altaffilmark{1,3}
    H.~K.~Fakhouri,\altaffilmark{1,3}
    U.~Feindt,\altaffilmark{9}
    D.~Fouchez,\altaffilmark{10}
    E.~Gangler,\altaffilmark{11}  
    B.~Hayden,\altaffilmark{1}
    W.~Hillebrandt,\altaffilmark{16}
    M.~Kowalski,\altaffilmark{9,12}
    P.-F.~Leget,\altaffilmark{11}
    S.~Lombardo,\altaffilmark{9}
    J.~Nordin,\altaffilmark{1,9}
    R.~Pain,\altaffilmark{4} 
    E.~Pecontal,\altaffilmark{13}
    R.~Pereira,\altaffilmark{2}
    S.~Perlmutter,\altaffilmark{1,3}
    D.~Rabinowitz,\altaffilmark{5}
    M.~Rigault,\altaffilmark{9} 
    D.~Rubin,\altaffilmark{1,14}
    K.~Runge,\altaffilmark{1}
    C.~Saunders,\altaffilmark{1,3}
    C.~Sofiatti,\altaffilmark{1,3} 
    N.~Suzuki,\altaffilmark{1}
    S.~Taubenberger,\altaffilmark{16}
    C.~Tao,\altaffilmark{6,10}
    R.~C.~Thomas,\altaffilmark{1} \\
    (The Nearby Supernova Factory)
}

@@

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be significantly
dependent on the spectral equivalent widths, and two independent color parameters.  One parameter, interpreted as due to extrinsic host-galaxy
dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
is inferred to have origins intrinsic to supernovae.  Our model explains features of external data, such as the wide range of inferred $R_V$ among
SNe~Ia, the low  $R_V$ of redder supernovae, the colors of SN~2014J, and the color-dependent residuals in Hubble diagrams.
\end{abstract}

\keywords{supernovae: genera; supernovae:SN 2014J}

@@

Supernova-frame synthetic photometry is generated for the top-hat filter system
described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the velocity of SiII$\lambda 6355$ as in \citet{chotard:thesis}.
Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}. [Confirm!]
The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.

@@

\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$v_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
 & (\AA) & (\AA)&  \colhead{(km s$^{-1}$)} & \multicolumn{5}{c}{}

@@

We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ velocity $v_{Si}$:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on an
extrinsic-color parameter $k$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 v_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 v_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 v_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 v_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 v_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ v_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma$ are the slopes that connect the extrinsic-color
parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$.
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other,
as confirmed by recalculation of the posterior after exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.

@@

In a Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior
\citep{Lewandowski20091989} and standard
deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
 $0.1$ and scale $0.1$ mag restricted to positive values.

\section{Results}
\label{results:sec}
The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
STAN \citep{stan}. STAN provides output statistics to assess
the convergence of the output Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
the Monte Carlo chains have not converged to the stationary posterior distribution.

@@

We find small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating their sensitivity to
$EW_{Si}$.  This validates our hypothesis that spectral indicators
are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $v_{Si}$) are consistent with zero within one sigma.
The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
values of zero signify no color changes associated with magnitude changes.
Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
We do not detect a significant association between
$v_{Si}$ and color.

@@

The best-fit distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
Although the posteriors of $\delta$ are close to Gaussian, $\delta_1-\delta_2$ can approach zero, resulting in the
elongated tail in negative  $R_{\delta X}$.
All values are negative and inconsistent with zero: a color excess in $B-V$ produces a brightening of the supernova.
The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
from $V$ to $I$,
a consequence
of which is that
a reddening in $B-V$ comes with a blueing in $V-R$.
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
more complicated underlying supernova physics.

@@

Our model predicts that internal and external effects for each supernova  conflate into an effective color excess
$E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
$A_{B, eff} = \gamma_1 k + \delta_1D$.
Recall that in our model the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrary
fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
Our model does not provide a unique value for the statistic $R_{B,eff} = A_{B, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.
However, the model can show that  $R_{B,eff}$  decreases on average with increasing effective color excess.

We plot $E_{eff}(B-V) + const$ versus
$A_{B, eff}$ for the SNf sample in Figure~\ref{rveff:fig}.
Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_1$.
The constant added to the effective color excess
corresponds to specifying a specific color as having zero extinction, and is chosen  qualitatively to form a ridge line 
bounding the high-extinction side of the data; the discussion that follows does not depend on the specific choice of the constant.
The right plot of Figure~\ref{rveff:fig} shows  how much more extinction (relatively) is
observed compared to the expected extinction from extrinsic dust for the corresponding effective color excess,
 $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
Over all effective color excesses the difference is capped by the ridge line, except for extremely
blue supernovae that lie slightly but noticeably above the ridge line.
However, with increasing effective color excess there is a broadening of the distribution toward lower observed extinctions.
A linear fit between $E_{eff}(B-V)$  and $\Delta A_B$ gives a slope of $-0.45 \pm 0.11$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/rveff.pdf}
   \includegraphics[width=2.8in]{output11/rveffres.pdf}
   \caption{Left: Effective color excess $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and effective $B$-band ``extinction''
$A_{B, eff} = \gamma_1 k + \delta_1D$ for the SNf sample.  Overplotted is the expected relationship for color-excess
purely due to the intrinsic $\gamma$ term.   The zero of  $E_{eff}(B-V)$  is shifted so that the  the extrinsic dust expectation qualitatively forms a ridge line
bounding the high-extinction side of the data.
Right:  The observed extinction compared to that expected  from extrinsic dust $\Delta A_B =  A_{B,eff}- \gamma_1 E_{eff}(B-V)$.
   \label{rveff:fig}}
\end{figure}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected for the infrequent selection of supernovae
heavily extinguished by host-galaxy dust.
Outliers  are also clearly distinguished in  $EW_{Ca}$--$v_{Si}$ space.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
$\Delta$.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $v_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$v_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
External $E_\gamma(B-V)$ dust is
most strongly correlated with $EW_{Si}$; recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy properties
\citep{2003MNRAS.340.1057S}.
The internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
indeed is not related to extrinsic dust.
An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}.

>>>>

\documentclass{aastex}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{lineno}

\linenumbers

@@

\title{Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory}
\author
{
    A.~G.~Kim,\altaffilmark{1}
    G.~Smadja,\altaffilmark{2} 
    G.~Aldering,\altaffilmark{1}
    P.~Antilogus,\altaffilmark{4}
    S.~Bailey,\altaffilmark{1}
    C.~Baltay,\altaffilmark{5}
    K.~Barbary,\altaffilmark{3}
    D.~Baugh,\altaffilmark{6}
    K.~Boone,\altaffilmark{1,3}
    S.~Bongard,\altaffilmark{4}
    C.~Buton,\altaffilmark{2}
    J.~Chen,\altaffilmark{6}
    N.~Chotard,\altaffilmark{2}
    Y.~Copin,\altaffilmark{2}
    P.~Fagrelius,\altaffilmark{1,3}
    H.~K.~Fakhouri,\altaffilmark{1,3}
    U.~Feindt,\altaffilmark{9}
    D.~Fouchez,\altaffilmark{10}
    E.~Gangler,\altaffilmark{11}  
    B.~Hayden,\altaffilmark{1}
    W.~Hillebrandt,\altaffilmark{16}
    M.~Kowalski,\altaffilmark{9,12}
    P.-F.~Leget,\altaffilmark{11}
    S.~Lombardo,\altaffilmark{9}
    J.~Nordin,\altaffilmark{1,9}
    R.~Pain,\altaffilmark{4} 
    E.~Pecontal,\altaffilmark{13}
    R.~Pereira,\altaffilmark{2}
    S.~Perlmutter,\altaffilmark{1,3}
    D.~Rabinowitz,\altaffilmark{5}
    M.~Rigault,\altaffilmark{9} 
    D.~Rubin,\altaffilmark{1,14}
    K.~Runge,\altaffilmark{1}
    C.~Saunders,\altaffilmark{1,3}
    C.~Sofiatti,\altaffilmark{1,3} 
    N.~Suzuki,\altaffilmark{1}
    S.~Taubenberger,\altaffilmark{16}
    C.~Tao,\altaffilmark{6,10}
    R.~C.~Thomas,\altaffilmark{1} \\
    (The Nearby Supernova Factory)
}

@@

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
dependent on the spectral equivalent widths, and two independent color parameters with better than 0.999 confidence.
One parameter, interpreted as due to extrinsic host-galaxy
dust extinction, is consistent with an $R_V=2.5$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: the wide range and
the low values of inferred $R_V$ among
SNe~Ia, and the colors of SN~2014J.
\end{abstract}

\keywords{supernovae: general; supernovae: SN 2014J}

@@

Supernova-frame synthetic photometry is generated for the top-hat filter system
described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the  velocity of SiII$\lambda 6355$ (expressed as the
observed location of the feature $\lambda_{Si} = (1+v_{Si}/c) 6355$\AA)
as in \citet{chotard:thesis}.
Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}. [Confirm!]
The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.

@@

\colhead{$n$} & \colhead{$EW_{Ca}$} & \colhead{$EW_{Si}$} & \colhead{$\lambda_{Si}$} & \colhead{$U$} & \colhead{$B$} & \colhead{$V$} & \colhead{$R$} & \colhead{$I$} \\
 & (\AA) & (\AA)&  \colhead{(\AA)} & \multicolumn{5}{c}{}

@@

We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ position $\lambda_{Si}$ (so also linear with $v_{Si}$):
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on an
extrinsic-color parameter $k$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma$ are the slopes that connect the extrinsic-color
parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$.
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other,
as confirmed by recalculation of the posterior after exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.

@@

In a Bayesian analysis the priors must be described.  A flat prior is used for all parameters except
for the covariance matrix $C_c$, which is constructed from a correlation matrix with  $\nu=4$  LKJ prior\footnote{
Visualization of the LKJ correlation distribution can be found in \url{http://www.psychstatistics.com/2014/12/27/d-lkj-priors/}.}
\citep{Lewandowski20091989} and standard
deviations $\sigma_i = \sqrt{C_{c,ii}}$ with a  Cauchy distribution prior with location
 $0.1$ and scale $0.1$ mag restricted to positive values.  (We find that imposing a stricter assumption of a
 diagonal covariance matrix, with no reference to a correlation matrix with LKJ prior, yields the same parameter distributions within
 uncertainty).

\section{Results}
\label{results:sec}
The posterior of the model parameters is evaluated using Hamiltonian Monte Carlo as implemented in
STAN \citep{stan}. STAN provides output statistics to assess
the convergence of the output Markov chains.  The output gives $\hat{R} \sim 1.0$ for all parameters, meaning there is no evidence for non-convergence.  The
output also gives  $N_{eff} \gg 100$ for all parameters, indicating that are all densely sampled.
Empirically, the confidence regions are localized and unimodal as is seen in  Figure~\ref{global:fig}.  We find no evidence that
the Monte Carlo chains have not converged to the stationary posterior distribution.
We have rurun the analysis with a variety of initial conditions, including one with all the $\gamma$'s and $\delta$'s equal to zero, except for a small positive 
$\gamma_0$ and small negative $\delta_0$ to satisfy our limit conditions.  Parameter credible intervals
remain consistent within uncertainty.

@@

We find small but significant non-zero values for $\alpha_0$ and $\alpha_4$, indicating that $EW_{Ca}$ is an indicator of $U$ and $I$
magnitudes.  All bands show larger and significant non-zero values for $\beta$, indicating their sensitivity to
$EW_{Si}$.  This validates our hypothesis that spectral indicators
are tracers of supernova absolute magnitude.  On the other hand, the values of $\eta$ (the coefficients attached to $\lambda_{Si}$) are consistent with zero within one sigma.
The effect of spectral parameters on color is shown in $\alpha_X/\alpha_V-1$,  $\beta_X/\beta_V-1$, and  $\eta_X/\eta_V-1$:
values of zero signify no color changes associated with magnitude changes.
Both $EW_{Ca}$ and $EW_{Ca}$ are associated with color changes though not in $B-V$ specifically.
We do not detect a significant association between
$\lambda_{Si}$ and color.

@@

None of the 4000 links of
our Monte Carlo chains for $\delta$ exceed 0 (see Figure~\ref{global:fig}), we thus claim detection of an affect of the
intrinsic parameter on supernova magnitudes
with probability $>3999/4000$. 
The posterior distributions for $R_{\delta X}=\frac{\delta_X}{\delta_1-\delta_2}$ are shown in Figure~\ref{rx:fig}.
Although the posteriors of $\delta$ are close to Gaussian, $\delta_1-\delta_2$ can approach zero, resulting in the
elongated tail in negative  $R_{\delta X}$.
All values are negative and inconsistent meaning a color excess in $B-V$ produces a brightening of the supernova.
The values of $\delta_X/\delta_V-1$ are not monotonic with color: they increase from the $U$ to $V$, and then decrease
from $V$ to $I$,
a consequence
of which is that
a reddening in $B-V$ comes with a blueing in $V-R$.
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G}, or a blackbody in the Raleigh-Jeans tail, and so may be indicative of
more complicated underlying supernova physics.

@@

Our model predicts that internal and external effects for each supernova  conflate into an effective color excess
$E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and $B$-band ``extinction''
$A_{V, eff} = \gamma_1 k + \delta_1D$.
Recall that in our model the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrary
fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$.
Our model does not provide a unique value for the statistic $R_{V,eff} = A_{V, eff} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.

To impose specificity for qualitative discussion, we add offsets to $A_{B, eff}$ and $E_{eff}(B-V)$ to  set the
blue/bright corner of the distribution to roughly $E_{eff}(B-V)=0$ and $A_{B, eff}=0$  as shown in Figure~\ref{rveff:fig}.
Overplotted is the expected extinction due to a pure extrinsic extinction with slope equal to $\gamma_2$.
The right plot of Figure~\ref{rveff:fig} shows 
the effective total-to-selective extinction $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
Over all effective color-excess, $R_{V,eff}$ is bounded by a maximum value.  At blue colors there is a wide range of $R_{eff,V}$
but with large uncertainties.  At redder colors, the spread in $R_{eff,V}$ decreases but the uncertainties also decrease to 
show a number of per-supernova
inconsistencies with the maximum bound.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/rveff.pdf}
   \includegraphics[width=2.8in]{output11/rveff2.pdf}
   \caption{Left: Effective color excess $E_{eff}(B-V) = E_\gamma(B-V) + E_\delta(B-V)$ and effective $B$-band ``extinction''
$A_{V, eff} = \gamma_1 k + \delta_1D$ for the SNfactory sample.  Overplotted is the expected relationship for color-excess
purely due to the intrinsic $\gamma$ term. 
Right:  The inferred $R_{V,eff} = A_{V, eff}/E_{eff}(B-V)$.
   \label{rveff:fig}}
\end{figure}

@@

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
Many outliers appear in the red tail of $E_\gamma(B-V)$, as would be expected for the infrequent selection of supernovae
heavily extinguished by host-galaxy dust.
Outliers  are also clearly distinguished in  $EW_{Ca}$--$\lambda_{Si}$ space.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$, as well as the grey offset
$\Delta$.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_\gamma(B-V)$, and $E_\delta(B-V)$ are given in the matrix
\begin{equation}
\begin{pmatrix}
1.000 & -0.012 & -0.031 & -0.026 & 0.070 & 0.002 \\
-0.012 & 1.000 & 0.128 & -0.331 & -0.064 & -0.004 \\
-0.031 & 0.128 & 1.000 & -0.182 & -0.155 & -0.024 \\
-0.026 & -0.331 & -0.182 & 1.000 & 0.018 & 0.036 \\
0.070 & -0.064 & -0.155 & 0.018 & 1.000 & 0.062 \\
0.002 & -0.004 & -0.024 & 0.036 & 0.062 & 1.000
\end{pmatrix}.
\end{equation}
Again  $EW_{Ca}$--$\lambda_{Si}$ is singled out, this time as having the strongest (anti-)correlation.  
External $E_\gamma(B-V)$ dust is
most strongly correlated with $EW_{Si}$; recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy properties
\citep{2003MNRAS.340.1057S}.
The internal $E_\delta(B-V)$  has no correlation  with internal parameters stronger than
0.04.  Although $E_\gamma(B-V)$ and $E_\delta(B-V)$ are determined simultaneously for each supernova from colors, they have a low correlation coefficient of 0.062;
this low correlation, and the broad distribution in $E_\delta(B-V)$ for low $E_\gamma(B-V)$,  indicate that what we have been calling intrinsic
indeed is not related to extrinsic dust.
An extensive analysis of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}.
